---
title: "DIAGRAM 2 basic graphic-1"
author: "xh"
date: "2017年7月21日"
# output: html_document
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# catalogue {.sidebar}
+ 1 折线图
    - R 自带
    - ggplot2
+ 2 条形图（含堆积）
    - R 自带
    - ggplot2
+ 3 直方图
    - R 自带
    - ggplot2
+ 4 饼图
    - R 自带
    - ggplot2
+ 5 散点图
    - R 自带
    - ggplot2   
+ 6 保存
    - R 自带
    - ggplot2     

-------------------------------------------------------------------------

# 1 line chart
## Column 1
### R


## Column 2
### ggplot2


-------------------------------------------------------------------------

# 2 bar chart {#anchor}
## Column 1
### R
```{r}
# install.packages('vcd')
library(vcd)
counts <- table(Arthritis$Improved)
```

#### 1 简单条形图 {.css_class}
```{r}
barplot(counts, main = 'Simplt Bar Plot',
        xlab = 'Improvement', ylab = 'Frequency')
```

#### 2 水平条形图
```{r}
# 水平条形图
barplot(counts, main = 'Horizontal Bar Plot',
        xlab = 'Frequency', ylab = 'Imporvement',
        horiz = TRUE)
```

## Column 2
### ggplot2
```{r}
require(ggplot2)
data(diamonds)
set.seed(42)
small <- diamonds[sample(nrow(diamonds), 1000), ]
```

```{r}
ggplot(small)+geom_bar(aes(x=clarity))
```


# 4 pie chart
## Column 1
### R
```{r}
par(mfrow = c(2,2))
slices <- c(10,12,4,16)
lbls <- c('US','UK','AU','GE')
```

```{r}
pie(slices, labels = lbls,
    main = 'Simple Pie Chart')
```

## Column 2
### ggplot2
```{r}
ggplot(small)+geom_bar(aes(x=factor(1),    
              fill=cut))+coord_polar(theta="y")
```

# 3 histogram chart
## Column 1
### R


## Column 2
### ggplot2



# 4 Kernel density chart
## Column 1
### R


## Column 2
### ggplot2



# 5 box chart
## Column 1
### R


## Column 2
### ggplot2



# 6 dot chart
## Column 1
### R


## Column 2
### ggplot2


# 7 save file
## Column 1
### R

```{r}
## Not run: ------------------------------------
# pdf(file="myplot.pdf")
# dev.off()

# png(file="myplot.png", bg="transparent")
# dev.off()

# jpeg(file="myplot.jpeg")
# dev.off()

# 其它：postscrept('plot.eps')

# 图片默认存放在getwd()，可通过setwd()改变

# 当数据图很多时，记得用paste（），
# for(i in genid){
#   pdf(file=paste(i,'.pdf',sep=''))
#   hist(get(i))
#   dev.off()
# }

## ---------------------------------------------
```


## Column 2
### ggplot2

**ggsave(filename, plot = last_plot(), device = NULL, path = NULL,**
    **scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),**
    **dpi = 300, limitsize = TRUE, ...)**

> + filename	
>     - File name to create on disk.
> + plot	
>     - Plot to save, defaults to last plot displayed.
> + device	
>     - Device to use. Can be either be a device function (e.g. png), or one of "eps", "ps", "tex" (pictex), "pdf", "jpeg", "tiff", "png", "bmp", "svg" or "wmf" (windows only).
> + path	
>     - Path to save plot to (combined with filename).
> + scale	
>     - Multiplicative scaling factor.
> + width, height, units	
>     - Plot size in units ("in", "cm", or "mm"). If not supplied, uses the size of current graphics device.
> + dpi	
>     - Plot resolution. Applies only to raster output types.

```{r}
## Not run: ------------------------------------
# ggplot(mtcars, aes(mpg, wt)) + geom_point()
# 
# ggsave("mtcars.pdf")
# ggsave("mtcars.png")
# 
# ggsave("mtcars.pdf", width = 4, height = 4)
# ggsave("mtcars.pdf", width = 20, height = 20, units = "cm")
# 
# unlink("mtcars.pdf")
# unlink("mtcars.png")
# 
# # specify device when saving to a file with unknown extension
# # (for example a server supplied temporary file)
# file <- tempfile()
# ggsave(file, device = "pdf")
# unlink(file)
## ---------------------------------------------
```
